---
title: "03 Automated Machine Learning with H20"
date: "2020-11-05"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

# First
```{r}
library(tidyverse)
library(GGally)
```

```{r}
employee_attrition_tbl <- read_csv("Attrition.txt")
employee_attrition_tbl %>%
  glimpse()
```


```{r}
plot_ggpairs <- function(data, color = NULL, density_alpha = 0.5) {
    
    color_expr <- enquo(color)
    
    if (rlang::quo_is_null(color_expr)) {
        
        g <- data %>%
            ggpairs(lower = "blank") 
        
    } else {
        
        color_name <- quo_name(color_expr)
        
        g <- data %>%
            ggpairs(mapping = aes_string(color = color_name), 
                    lower = "blank", legend = 1,
                    diag = list(continuous = wrap("densityDiag", 
                                                  alpha = density_alpha))) +
            theme(legend.position = "bottom")
    }
    
    return(g)
    
}
```


```{r}
plot <- employee_attrition_tbl %>%
    select(Attrition, MonthlyIncome, PercentSalaryHike, StockOptionLevel, EnvironmentSatisfaction, WorkLifeBalance, JobInvolvement, OverTime, TrainingTimesLastYear, YearsAtCompany, YearsSinceLastPromotion) %>%
  plot_ggpairs(color = Attrition)
  ggsave("asd.png",plot, width = 15, height = 15)
  plot
```
**IMPORTANT:** You can delete everything in here and start fresh. You might want to start by not deleting anything above this line until you know what that stuff is doing.

1. Compensation Features
  What can you deduce about the interaction between Monthly Income and Attrition?
  c. Those that are leaving have a lower Monthly Income

2. Compensation Features
  What can you deduce about the interaction between Percent Salary Hike and Attrition?
  d. It's difficult to deduce anything based on the visualization

3. Compensation Features
  What can you deduce about the interaction between Stock Option Level and Attrition?
  b. Those that are staying have a higher stock option level

4. Survey Results
  What can you deduce about the interaction between Environment Satisfaction and Attrition?
  a. A higher proportion of those leaving have a low environment satisfaction level
  
5. Survey Results
  What can you deduce about the interaction between Work Life Balance and Attrition
  b. Those that are staying have a higher density of 2's and 3'
  
6. Performance Data
  What Can you deduce about the interaction between Job Involvement and Attrition?
  a. Those that are leaving have a lower density of 3's and 4's
  
7. Work-Life Features
  What can you deduce about the interaction between Over Time and Attrition?
  a The proportion of those leaving that are working Over Time are high compared to those that are not leaving
  
8. Training and Education
  What can you deduce about the interaction between Training Times Last Year and Attrition
  c It's difficult to deduce anything based on the visualization
  
9. Time-Based Features
  What can you deduce about the interaction between Years At Company and Attrition
  b People that leave tend to have less working years at the company

10. Time-Based Features
  What can you deduce about the interaction between Years Since Last Promotion and Attrition?
  c. It's difficult to deduce anything based on the visualization

